### 2022-04-02 manuscript.tex
Update docx.yaml [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/43766a9c6b43fa547b7d571ee8496e8e2f89912f.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/43766a9c6b43fa547b7d571ee8496e8e2f89912f/checks
https://github.com/scherzerthesis/thesis/actions/runs/2082320372

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/0fa019fc01a326428db51f405b30eb6701837e33/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/0fa019fc01a326428db51f405b30eb6701837e33}{scherzerthesis/thesis@0fa019f}
on April 2, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/43766a9c6b43fa547b7d571ee8496e8e2f89912f/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/43766a9c6b43fa547b7d571ee8496e8e2f89912f}{scherzerthesis/thesis@43766a9}
on April 2, 2022.
